Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-06 Grassmannian_cells.tex
Section 5.1 edits

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above:
\begin{equation}
  \label{eq:truncated CC}
  \Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\[\ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},\]
where $\tilde K_m=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\begin{equation}
  \label{eq:truncated CC2}
  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

%\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
%  Lemma~\ref{AR} can be generalized to the cases $m\leq 2$.
%  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence. 
%\end{remark}
In the following, we freely use the notation and conventions of Section~\ref{sec:RepK(n)}.
For $m\ge1$, Theorem~\ref{thm:truncpp} shows that up to isomorphism the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ for $V\in\Gr(H_m)$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
In particular, fixing $\dim V=r$, we construct a 2-quiver $\cQ_{m+1}^{[r]}$ whose strong successor closed are in one-to-one correspondence with the cells of quiver Grassmannians of~$P_{m+1}^V$.

@@

The 2-quiver $\cQ_2^{[r]}$ associated to the (truncated) preprojective $\tilde P_2^{[r]}$ has underlying quiver $Q_2^{[r]}:=Q_1^\sigma\sqcup\coprod\limits_{i=1}^{n-r} Q_{1,i}$, where the single vertex of the quiver $Q_1^\sigma$ is associated to the vertex $(2,e)$ of $\widetilde{K(n)}$, and has 2-arrows (colored red) as in the figure below:
\[\begin{tikzpicture}
  \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
  \draw (0,0) node (Vr) {$(1,\alpha_{n-r})$} +(.8,-.9) node {\footnotesize$ \mathcal Q_2^{[r]}$} +(3,0) node (Vr1) {$(1,\alpha_{n-r+1})$}+(3.8,-.9) node (Lr1) {\footnotesize$ \mathcal Q_2^{[r+1]}$} +(6,0) node (Vx) {$\dots$} +(9,.15) node (V2) {$(1,\alpha_{2})$} +(9.8,-.75) node (L2) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,.45) node (V1) {$(1,\alpha_1)$}  +(14,.45) node (V0) {$(2,e)$} +(12.8,-.35) node (L1) {\footnotesize$\mathcal Q_2^{[n-1]}$};

@@

\begin{remark}
  \label{rem:2-arrows Q2}
  The 2-arrows of $\cQ_2$ should be viewed as a reflection of the isomorphism
  \begin{equation*}
    \label{eq:case2}
    \Ext(P_2,P_1)
    \cong\bigoplus_{i=1}^n \Ext(\tilde P_2,\tilde P_{1,i})
    \cong\big\langle (2,1)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=1,\ldots,n\big\rangle
  \end{equation*}
  and the inclusions of $\cQ_2^{[t]}$ in $\cQ_2^{[r]}$ for $t\ge r$ as a reflection of the surjections $\Ext(P_2^{[t]},P_1)\onto\Ext(P_2^{[r]},P_1)$.
  In particular, the isomorphism \eqref{eq:case2} can be used with these surjections to obtain compatible bases for each $\Ext(P_2^{[r]},P_1)$.
\end{remark}
The $2$-quiver $\mathcal Q_2^{[r]}$ given above is clearly equivalent to the support quiver \eqref{coeff} thought of as a 2-quiver with no 2-arrows:
\begin{align}
  \label{coeff}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-r}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-r})}
\end{align}
In this way we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
In order to keep the illustrations and combinatorics simple, we will abuse notation and denote the support quiver \eqref{coeff} by $\mathcal Q_{2}^{[r]}$, working instead with this 2-quiver.
In this way we may define the translated 2-quivers $\cQ_{2,i}$ (resp.\ $\cQ_{2,i}^{[r]}$) as those obtained from $\cQ_2$ (resp.\ $\cQ_2^{[r]}$) by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.

@@

  For $m\ge2$, we may apply Theorem~\ref{covering} together with Lemma~\ref{le:properties} and the Auslander-Reiten formula to get an isomorphism 
  \begin{align}
    \label{eq:homext} 
    \Ext\big(P_{m+1}^{[r]},P_m\big)
    \cong\bigoplus_{i=r+1}^n \Ext\big(\tilde P_{m+1}^{[r]},\tilde P_{m,i}\big)
    \cong\bigoplus_{i=r+1}^n \Hom\big(\tilde P_{m,i},\tau\tilde P_{m+1}^{[r]}\big).
  \end{align}
\end{remark}

\begin{remark}
  Recall that $\tilde P_3^{[n-1]}=\alpha_n^{-1}.\tilde P_2^{[1]}$.
  Moreover, (\ref{eq:homext}) for $m=3$ yields 
  \[\Ext(P_2^{[1]},P_2)\cong\Ext(P_3^{[n-1]},P_2)\cong\bigoplus_{i=1}^{n-1}\Ext(\tilde P_3^{[n-1]},\alpha_i^{-1}\tilde P_2).\]
  This decomposition induces a basis of $\Ext(P_3^{[n-1]},P_2)$, each basis element given by the linear map 
  \[(2,\alpha_n^{-1})\xlongrightarrow{\alpha_n}(1,e)\in\Hom_{\CC}((\tilde P_2^{[1]})_{(2,\alpha_n^{-1})},(\alpha_i^{-1}\tilde P_2)_{(1,e)})\]
  for $i=1,\ldots,n-1$.
  Recall that the representation $\tau\tilde P_3^{[k]}$ is given by 
  \[ \xymatrix@R40pt@C10pt{&(1,e)&\\ (2,\alpha_1^{-1})\ar_{\alpha_1}[ru]&\cdots&(2,\alpha_{k}^{-1})\ar^{\alpha_{k}}[lu]}.\]
  Note that the image of the homomorphism corresponding to the basis element spanning 
  \[\Hom(\alpha_{k}^{-1}.\tilde P_{2},\tau\tilde P_{m}^{[k]})\cong\Ext(\tilde P_3^{[n-1]},\alpha_k^{-1}\tilde P_2)\]
  corresponds to the subquiver $(2,\alpha_k^{-1})\xrightarrow{\alpha_k} (1,e)$.
  This translates to the fact that $\cQ_3^{[k]}$ is glued to the image of the homomorphism $\tilde P_{2,k}\to \tau \tilde P_3^{[k]}$ which is of dimension $(1,1)$.

  This gives a justification for the original definition of the 2-arrows in $\cQ_3^{[r]}$.

    In view of Corollary~\ref{cor:perpendicular}, we have also an isomorphism 
    \[\Ext\big(\tilde P_{m+1}^{[k]},\tilde P_{m,k}\big)\cong\Ext\big(\tilde P_{m+1}^{[k]},\tau\tilde P_{m+1}^{[k]}\big).\]
    These isomorphisms will also be present in the structure of the $2$-quivers $\cQ_{m+1}^{[k]}$.
    Finally note that there exists a short exact sequence
    \[\ses{\Hom(P_m,P_m)}{\Ext\big(P_{m+1}^{[k]},P_m\big)}{\Ext\big(P_{m+1}^{[k+1]},P_m\big)}.\]
    Thus a basis of $\Ext\big(P_{m+1}^{[k]},P_m\big)$ can be obtained by taking the last $k$ basis elements of a basis of $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
\end{remark}

The next step is to define the $2$-quivers $\cQ^{[k]}_3$ of the (truncated) preprojective lifts $\tilde P^{[k]}_3$ whence the remaining $2$-quivers attached to the (truncated) preprojectives $\tilde P_m^{[k]}$ can be obtained recursively.
First, we define
\[\cQ_3^{[n-1]}:=\alpha_{n}^{-1}.\cQ_2^{[1]},\]
i.e. we translate all vertices -- understood as vertices of $\widetilde{K(n)}$ -- and (2-)arrows by $\alpha_n^{-1}$.
Then $\cQ_3^{[k]}$ can be found as a sub-2-quiver of $\cQ_3$ which is constructed recursively by connecting $\cQ_3^{[i]}$ to $\cQ_{2,i}$ for $i=n-1,\ldots, 1$ in the following way: \\
\[
\begin{tikzpicture}[scale=1.35]
  \draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
  \draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$\alpha_1$};
  \draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$\alpha_2$};
  \draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n-1}$};
  \draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$\alpha_{n}$};

\end{tikzpicture}
\] 
To avoid cluttering the diagram, we did not label the vertices in the illustration.
Observe that the middle vertex of $\mathcal Q_3^{[n-1]}$ corresponds to $(2,\alpha_n^{-1})$ and that the target of the $2$-arrow, again colored red, into $\cQ_{2,n-1}$ is the vertex corresponding to $(1,e)$ of $\widetilde{K(n)}$.
In general, the 2-arrow from $\cQ_3^{[i]}$ into $\cQ_{2,i}$ has target the vertex corresponding to $(1,e)$ in $\widetilde{K(n)}$.
We again define translated versions $\cQ_{3,i}:=\alpha_i.\cQ_3$ of $\cQ_3$ which again means that we translate $\cQ_{3}$ as a union subquiver contained in $\widetilde{K(n)}$.

>>>>

We will apply this result in the setting of the truncated preprojective lifts from Lemma~\ref{le:homdecomposition}.
Fix $m\ge1$.
For subsets $J\subsetneq I\subsetneq\{1,\ldots,n\}$ with $I\setminus J=\{j\}$, Lemma~\ref{le:properties}.(1) provides a short exact sequence 
\begin{equation}
  \label{eq:truncated ses}
  \ses{\tilde P_{m,j}}{\tilde P_{m+1}^J}{\tilde P_{m+1}^I}
\end{equation}
which induces a map between quiver Grassmannians as above:
\begin{equation}
  \label{eq:truncated CC}
  \Psi_{m+1,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_{m,j})\times\Gr^{\tilde Q}_\tbfg(\tilde P_{m+1}^I).
\end{equation}
To understand the fibers of this map for $m\ge2$, we will need to make use of another map between quiver Grassmannians coming out of Lemma~\ref{le:special subrepresentations}.
Here we consider the short exact sequence 
\begin{equation}
  \label{eq:tau sequence}
  \ses{\tilde P_m(I,j)}{\tilde P_{m,j}}{\tilde K_m},
\end{equation}
where $\tilde K_m=\tilde K_m(I)=\tau\tilde P_{m+1}^I$ for $m\ge3$ and $\tilde K_2=\tilde K_2(I,j)$ is the representation in \eqref{eq:special case} from Remark~\ref{rem:special case}.
Then in the same way as above we obtain the map
\begin{equation}
  \label{eq:truncated CC2}
  \Phi_{m,I,j}:\Gr^{\tilde Q}_\tbfe(\tilde P_{m,j})\to\bigsqcup_{\tbff+\tbfg=\tbfe} \Gr^{\tilde Q}_\tbff(\tilde P_m(I,j))\times\Gr^{\tilde Q}_\tbfg(\tilde K_m).
\end{equation}
\begin{proposition}
  \label{quotient}
  For $m\geq 2$ and a nonempty subset $I\subsetneq\{1,\ldots,n\}$.
  The following hold for any $j\in I$:
  \begin{enumerate}
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is not empty if and only if $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
    \item The fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ is empty if and only if $\Phi_{m,I,j}(U)=(U,0)$, i.e.\ $U$ is already a subrepresentation of $\tilde P_m(I,j)$.
  \end{enumerate} 
\end{proposition}
\begin{proof}
  Any subrepresentation $U\subset\tilde P_{m,j}$ produces an exact sequence
  \[\xymatrix{\Ext(\tilde P_{m+1}^I,U)\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ar[r] &\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)\ar[r] & 0}.\]
  But note that the fiber $\Psi_{m+1,I,j}^{-1}(U,\tilde P_{m+1}^I)$ being nonempty gives rise to a pushout diagram
  \[\xymatrix{0\ar[r]& U\ar[r]\ar[d]\ar@{}[dr]|(.3){\ulcorner} & U'\ar[d]\ar[r]& \tilde P_{m+1}^I\ar[r]\ar@{=}[d]& 0\\
    0\ar[r] &\tilde P_{m,j}\ar[r] &  \tilde P_{m+1}^J\ar[r] & \tilde P_{m+1}^I\ar[r] & 0}\]
  in which the bottom row is not split by Lemma~\ref{le:properties}.(4).
  This implies that the map 
  \[\Ext(\tilde P_{m+1}^I,U)\to\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\]
  is surjective and thus $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j}/U)=0$.
  This argument can be reversed and thus (1) holds.

@@

%\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
%  Lemma~\ref{AR} can be generalized to the cases $m\leq 2$.
%  The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence. 
%\end{remark}
In the following, we freely use the notation and conventions of Section~\ref{sec:RepK(n)}.
For $m\ge1$, Theorem~\ref{thm:truncpp} shows that up to isomorphism the quiver Grassmannians $\Gr_\bfe(P_{m+1}^V)$ of arbitrary truncated preprojective representations $P_{m+1}^V$ for $V\in\Gr(H_m)$ only depend on $\bfe$ and $\udim P_{m+1}^V$.
In particular, fixing $\dim V=r$, we construct a 2-quiver $\cQ_{m+1}^{[r]}$ whose strong successor closed subsets are in one-to-one correspondence with the cells of quiver Grassmannians of~$P_{m+1}^V$.

@@

The 2-quiver $\cQ_2^{[r]}$ associated to $\tilde P_2^{[r]}$ has underlying quiver $Q_2^{[r]}:=Q_1^\sigma\sqcup\coprod\limits_{i=1}^{n-r} Q_{1,i}$, where the single vertex of the quiver $Q_1^\sigma$ is associated to the vertex $(2,e)$ of $\widetilde{K(n)}$, and has 2-arrows (colored red) as in the figure below:
\[\begin{tikzpicture}
  \tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
  \draw (0,0) node (Vr) {$(1,\alpha_{n-r})$} +(.8,-.9) node {\footnotesize$ \mathcal Q_2^{[r]}$} +(3,0) node (Vr1) {$(1,\alpha_{n-r+1})$}+(3.8,-.9) node (Lr1) {\footnotesize$ \mathcal Q_2^{[r+1]}$} +(6,0) node (Vx) {$\dots$} +(9,.15) node (V2) {$(1,\alpha_{2})$} +(9.8,-.75) node (L2) {\footnotesize$ \mathcal Q_2^{[n-2]}$}+(11.5,.45) node (V1) {$(1,\alpha_1)$}  +(14,.45) node (V0) {$(2,e)$} +(12.8,-.35) node (L1) {\footnotesize$\mathcal Q_2^{[n-1]}$};

@@

\begin{remark}
  \label{rem:2-arrows Q2}
  The 2-arrows of $\cQ_2$ should be viewed as a reflection of the isomorphism
  \begin{equation}
    \label{eq:case2}
    \Ext(P_2,P_1)
    \cong\bigoplus_{i=1}^n \Ext(\tilde P_2,\tilde P_{1,i})
    \cong\big\langle (2,e)\xrightarrow{\alpha_i}(1,\alpha_i)\mid i=1,\ldots,n\big\rangle
  \end{equation}
  and the inclusions of $\cQ_2^{[t]}$ in $\cQ_2^{[r]}$ for $t\ge r$ as a reflection of the surjections $\Ext(P_2^{[t]},P_1)\onto\Ext(P_2^{[r]},P_1)$.
  In particular, the isomorphism \eqref{eq:case2} can be used with these surjections to obtain compatible bases for each $\Ext(P_2^{[r]},P_1)$.
\end{remark}
The $2$-quiver $\mathcal Q_2^{[r]}$ given above is clearly equivalent to the support quiver \eqref{coeff} thought of as a 2-quiver with no 2-arrows:
\begin{align}
  \label{coeff}
    \xymatrix@R40pt@C10pt{&(2,e)\ar_{\alpha_1}[ld]\ar^{\alpha_{n-r}}[rd]&\\ (1,\alpha_1)&\cdots&(1,\alpha_{n-r})}
\end{align}
In this way we may think of $\cQ_2^{[r]}$ as a coefficient quiver of $\tilde P_2^{[r]}$ or of $P_2^V$ for $V\in\Gr(H_1)$ with $\dim V=r$.
In order to keep the illustrations and combinatorics simple, we will abuse notation and denote the support quiver \eqref{coeff} by $\mathcal Q_{2}^{[r]}$, working instead with this 2-quiver.
In this way we may define the translated 2-quivers $\cQ_{2,i}$ (resp.\ $\cQ_{2,i}^{[r]}$) as those obtained from $\cQ_2$ (resp.\ $\cQ_2^{[r]}$) by translating all vertices and ($2$-)arrows by $\alpha_i^{-1}$.

@@

  For $m\ge2$, we may apply Theorem~\ref{covering} together with Lemma~\ref{le:properties} and the Auslander-Reiten formula to get an isomorphism 
  \begin{align}
    \label{eq:homext} 
    \Ext\big(P_{m+1}^{[r]},P_m\big)
    \cong\bigoplus_{i=r+1}^n \Ext\big(\tilde P_{m+1}^{[r]},\tilde P_{m,i}\big)
    \cong\bigoplus_{i=r+1}^n \Hom\big(\tilde P_{m,i},\tau\tilde P_{m+1}^{[r]}\big).
  \end{align}
  The image of a nonzero map $\tilde P_{m,i}\to\tau\tilde P_{m+1}^{[r]}$ is the representation $\tilde K_m$ from the appropriate sequence \eqref{eq:tau sequence}.
  Such a map is surjective if $m\ge3$ and for $m=2$ has image with support quiver $(2,\alpha_i^{-1})\xrightarrow{\alpha_i} (1,e)$.
  In view of Corollary~\ref{cor:perpendicular}, the sequence \eqref{eq:tau sequence} gives rise to an isomorphism 
  \[\Ext\big(\tilde P_{m+1}^{[r]},\tilde P_{m,i}\big)\cong\Ext\big(\tilde P_{m+1}^{[r]},\tilde K_m\big).\]

  Finally note for $0\le r\le n-2$ that there exists a short exact sequence
  \[\ses{\Hom(P_m,P_m)}{\Ext\big(P_{m+1}^{[r]},P_m\big)}{\Ext\big(P_{m+1}^{[r+1]},P_m\big)}.\]
  Thus a basis of $\Ext\big(P_{m+1}^{[r]},P_m\big)$ can be obtained by taking the last $r$ elements of a basis for $\Ext\big(P_{m+1}^{[n-1]},P_m\big)$.
  The choice of 2-arrows in $\cQ_{m+1}^{[r]}$ should be viewed as a combinatorial shadow of the isomorphisms above.
\end{remark}

We are now ready to define the 2-quivers $\cQ_{m+1}^{[r]}$ for $m\ge3$.
This will be by induction, so assume we have already constructed the 2-quivers $\cQ_m^{[s]}$ for $0\le s\le n-1$ and define the 2-quivers $\cQ_{m,i}^{[s]}:=\alpha_i^{(-1)^{m+1}}.\cQ_m^{[s]}$ for $1\le i\le n$. 
Then we may take the underlying quiver of $\cQ_{m+1}^{[r]}$ to be
\[Q_{m+1}^{[r]}:=
  \begin{cases}
    Q_{m,n}^{[1]}\sqcup\coprod\limits_{i=r+1}^{n-1} Q_{m,i} & \text{if $m$ is even;}\\
    Q_{m,1}^{[1]}\sqcup\coprod\limits_{i=2}^{n-r} Q_{m,i} & \text{if $m$ is odd.}
  \end{cases}\]
For $r<s<n$, there is a 2-arrow $V_s:\Gamma_s(1)\to\Gamma_s(2)$ of $\cQ_{m+1}^{[r]}$ given by $\Gamma_s(1)=Q_{m+1}^{[s]}\subset Q_{m+1}^{[r]}$ with $\Gamma_s(2)\subset Q_{m,s}$ the subquiver $Q_{m-1}^{[s]}\subset Q_{m-1}=Q_{m-1,(s,s)}\subset Q_{m,s}$.
\begin{remark}
  For $m\geq 3$, the truncated preprojective $\tau\tilde P_{m+1}^{[s]}\cong\tilde P_{m-1}^{[s]}$ can uniquely be found as a quotient of $\tilde P_{m,s}$.
  This is reflected in the structure of the $2$-quivers as we can find $\cQ_{m-1}^{[s]}$ as a subquiver of $\cQ_{m,s}$.
  In the diagrams for 2-quivers given here, this sub-2-quiver can be found at the very right of the $2$-quiver $\mathcal Q_{m,s}$.
\end{remark}

\begin{flushleft}
\begin{tikzpicture}[scale=0.97]
\draw (0,4) node (A1) {\footnotesize$Q_{m-1,1}$}
  +(0,-1.2) node (PM) {\footnotesize$\mathcal Q_{m,r}$}
  +(1.65,0) node (B1) {\footnotesize$Q_{m-1,2}$}
  +(1.65,-1.1) node (P11) {\footnotesize$\mathcal Q_{m}^{[1]}$}
  +(3,0) node (B11) {\footnotesize$\dots$}
  +(4.55,0) node (D1) {\footnotesize$Q_{m-1,n-1}$}
  +(4.55,-1) node (P41) {\footnotesize$\mathcal Q_{m}^{[n-2]}$}
  +(6.4,0) node (E1) {\footnotesize$Q_{m-2,2}$}
  +(6.4,-.9) node (P51) {\footnotesize$\mathcal Q_{m-1}^{[1]}$}
  +(7.75,0) node (A1b) {\footnotesize$\dots$}
  +(9.6,0) node (B1b) {\footnotesize$Q_{m-2,r+1}$}
  +(9.6,-.8) node (P11b) {\footnotesize$\mathcal Q_{m-1}^{[r]}$}
  +(11.2,0) node (B11b) {\footnotesize$\dots$}
  +(12.8,0) node (D1b) {\footnotesize$Q_{m-2,n-1}$}
  +(12.8,-.6) node (P41b) {\footnotesize$\mathcal Q_{m-1}^{[n-2]}$}
  +(14.4,0) node (E1b) {\footnotesize$\mathcal Q^{[n-1]}_{m-2}$};
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[implies-,double equal sign distance,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q11)--(B11b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q21)--(B1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q31)--(A1b) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q41)--(E1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q51)--(D1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q61)--(B11) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q71)--(B1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q81)--(A1) node[pos=.5,above] {};

\draw (4.45,0) node (B) {$\mathcal Q_{m,r+1}$}+(0,-.8) node (P1) {\footnotesize$\mathcal Q_{m+1}^{[r]}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$\mathcal Q_{m,n-2}$} +(5,-.7) node (P3) {\footnotesize$\mathcal Q_{m+1}^{[n-3]}$}+(7.5,0) node (D) {$\mathcal Q_{m,n-1}$}  +(10,0) node (E) {$\mathcal Q_{m+1}^{[n-1]}$} +(7.5,-.6) node (P4) {\footnotesize$\mathcal Q_{m+1}^{[n-2]}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

\draw[implies-,double equal sign distance,red] (D)--(E) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q1)--(C) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q2)--(B1) node[pos=.5,above] {};
\draw[-implies,double equal sign distance,red] (Q2b)--(B) node[pos=.5,above] {};

\node (PMK) [draw=black,fit={(Q2b) (B)}]{};
\draw[-implies,double equal sign distance,red,thick] (PMK)--(P11b);
\end{tikzpicture}
\\
\end{flushleft}
\noindent 
As already mentioned two different vertices of $\mathcal Q_m^{[r]}$ can correspond to the same vertex of $\widetilde{K(n)}$.
Writing dimension vectors $\tbfe\in\NN^{\widetilde{K(n)_0}}$ as $\tbfe=\sum_{q\in \widetilde{K(n)_0}}\tbfe_q\cdot q$, the dimension types $\tbfe (\beta)$ and  $\bfe (\beta)$ of a subset $\beta\subset (\mathcal Q_m^{[r]})_0$ are defined by
\[\tbfe (\beta)=\sum_{q\in\beta} \tilde q\in\NN^{\widetilde{K(n)_0}},\quad \bfe (\beta)=G\big(\tbfe(\beta)\big)\in\NN^{K(n)_0},\]
where $\tilde q\in\widetilde{K(n)}_0$ is the vertex which corresponds to $q\in \beta\subset (\mathcal Q_m^{[r]})_0$.

\begin{theorem}\mbox{}
  \label{thm:2quivercells}
  \begin{enumerate}
    \item The cells of the cell decomposition of $\Gr_\tbfe\big(\tilde P_m^{[r]}\big)$ (resp. $Gr_\bfe\big(P_m^{[r]}\big)$) induced by Theorem \ref{cellscover} can be labeled by strong successor closed subsets $\beta\subset\mathcal Q_m^{[r]}$ of dimension type $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp. $\bfe\in\NN^{K(n)_0}$) yielding a one-to-one correspondence between cells and strong successor closed subsets.
    \item  For $\tbfe\in\NN^{\widetilde{K(n)_0}}$ (resp. $\bfe\in\NN^{K(n)_0}$), the Euler characteristic $\chi(\Gr_{\tbfe }(\tilde P_m^{[r]}))$ (resp. $\chi(\Gr_{\bfe }(P_m^{[r]}))$) is given by the number of strong successor closed subsets of dimension type $\tbfe$  (resp. $\bfe$) of the $2$-quiver of $\mathcal Q_m^{[r]}$.
  \end{enumerate}
\end{theorem}
\begin{proof}
The results of Sections~\ref{sec:bb} and \ref{torusaction} imply that the statements in parentheses follow from the respective results for the lifted representations. Moreover, the second result follows from the first one.

We proceed by induction on $m$ and $r$. The case of the representation $\tilde P_1$ is trivial. We have $(\tilde P_2^{[r]})_q\in\{0,1\}$ for all $q\in\widetilde{K(n)}$, whence the  subrepresentations are in one-to-one correspondence with the successor closed subsets of the quiver (\ref{coeff}) which is equivalent to  $\mathcal Q_2^{[r]}$ . Equivalently, we have $\Gr_{\tbfe}(\tilde P_2^{[r]})\in\{\varnothing,\{\pt\}\}$ such that $\Gr_{\tbfe}(\tilde P_2^{[r]})=\{\pt\}$ if and only if $\tbfe\subset \mathcal Q_2^{[r]}$ is strong successor closed.

  Thus assume that the claim is true for $\tilde P_m$  and $\tilde P_{m+1}^{[r]}$ and consider the short exact sequence
  \[
    \ses{\tilde P_m}{\tilde P_{m+1}^{[r-1]}}{\tilde P_{m+1}^{[r]}}.
  \]
  We have $(\mathcal Q_{m+1}^{[r-1]})_0=(\mathcal Q_{m+1}^{[r]})_0\coprod{}(\mathcal Q_{m,r})_0$.
	Let $\beta_1\coprod\beta_2\subset (\mathcal Q_{m+1}^{[r-1]})_0\coprod{}(\mathcal Q_{m,r})_0$ be a pair of strong successor closed subsets which gives rise to a pair of non-empty cells by induction hypothesis.
 % Denote by $d(\beta_1+\beta_2)$ the dimension vector corresponding to this subset.
  By Proposition~\ref{quotient}, the fibre over the pair of cells corresponding to $\beta_1\coprod\beta_2$ is empty if and only if $\beta_2=(\mathcal Q_{m+1}^{[r]})_0$ and $\beta_1\cap(\mathcal Q_{m-1}^{[r]})_0=\varnothing$ where $\mathcal Q_{m-1}^{[r]}$ is considered as a $2$-quiver of $\mathcal Q_{m,r}$.
  But this is precisely the condition on $\beta_1\coprod\beta_2$ to be strong successor closed as $\mathcal Q_{m+1}^{[r]}$ is connected to $\mathcal Q_{m-1}^{[r]}$ by a $2$-arrow. This shows the first claim.
\end{proof}
